\sysfull

### 2018-04-10 paper/intro.tex
add task splitting, correct the provided example

Unfortunately, naively merging two atomic tasks might produce a non-atomic task, that may leave non-volatile memory inconsistent after a partial execution. A merge breaks atomicity when atomic merged tasks form a \emph{write-after-read (WAR)} dependency---for instance if two tasks \texttt{\{x++\}; \{vector[x]=v;\}} are merged and if the power failure occurs after \texttt{x++}, the value \texttt{x} will be increased twice when the merged task is restarted, that leads to an inconsistency.
%
%variables in non-volatile memory at \emph{run-time} that can
%break the atomicity of the \emph{virtual task}. Consider the
%example depicted in Fig.~\ref{fig:virtualization}: Tasks 1,
%2 and 3 being executed consecutively. All tasks in this
%example are atomic since they do not have WAR dependency on
%the persistent variables they are accessing, e.g. \emph{x}
%is only read and \emph{y} is only written within Task 1.
%Now, suppose three tasks have been virtualized into a single
%one at run-time, namely Task 4: since \emph{x} is now first
%\emph{read} and then \emph{written}, a WAR dependency on
%\emph{x} is introduced dynamically at
%run-time---unfortunately Task 4 is \emph{no more atomic}
%since its re-execution will not always produce the same
%results.
%
Although WAR dependencies introduced by the \emph{static} task division can be eliminated at compile time~\cite{alpaca}, those introduced \emph{dynamically} at
run-time cannot. To maintain memory consistency in merged tasks, we propose a
mechanism for \emph{memory virtualization} that buffers the updates to non-volatile variables in volatile memory before committing them at the dynamic task boundary.
%
%Therefore, we require a \emph{new execution
%model} that keeps each virtual task atomic by committing the
%modified persistent variables at the boundary defined
%dynamically at run-time---keeping the non-volatile memory
%unmodified upon a power-interrupt and preserving its
%consistency.

@@

\begin{itemize}
	\item Two adaptive coalescing strategies for selecting boundaries to coalesce based on past execution behaviour;
	\item Software memory virtualisation for transiently-powered devices that preserves atomicity of coalesced tasks;
	\item Compiler pass for automatic decomposition into small atomic tasks for adaptive coalescing at runtime.
\end{itemize}

>>>>

Unfortunately, naively merging two atomic tasks might produce a non-atomic task, that may leave non-volatile memory inconsistent after a partial execution. A merge breaks atomicity when atomic merged tasks form a \emph{write-after-read (WAR)} dependency---for instance if two tasks \texttt{\{x=y+1\}; \{y=x;\}} are merged and if the power failure occurs after \texttt{x=y}, the value \texttt{x} will be increased twice when the merged task is restarted, that leads to an inconsistency.
%
%variables in non-volatile memory at \emph{run-time} that can
%break the atomicity of the \emph{virtual task}. Consider the
%example depicted in Fig.~\ref{fig:virtualization}: Tasks 1,
%2 and 3 being executed consecutively. All tasks in this
%example are atomic since they do not have WAR dependency on
%the persistent variables they are accessing, e.g. \emph{x}
%is only read and \emph{y} is only written within Task 1.
%Now, suppose three tasks have been virtualized into a single
%one at run-time, namely Task 4: since \emph{x} is now first
%\emph{read} and then \emph{written}, a WAR dependency on
%\emph{x} is introduced dynamically at
%run-time---unfortunately Task 4 is \emph{no more atomic}
%since its re-execution will not always produce the same
%results.
%
Although WAR dependencies introduced by the \emph{static} task division can be eliminated at compile time~\cite{alpaca}, those introduced \emph{dynamically} at
run-time cannot. To maintain memory consistency in merged tasks, we propose a
mechanism for \emph{memory virtualization} that buffers the updates to non-volatile variables in volatile memory before committing them at the dynamic task boundary.
%
%Therefore, we require a \emph{new execution
%model} that keeps each virtual task atomic by committing the
%modified persistent variables at the boundary defined
%dynamically at run-time---keeping the non-volatile memory
%unmodified upon a power-interrupt and preserving its
%consistency.

\textbf{Task Splitting}: The static task execution model assumes that a single task execution is guaranteed by the hardware. If this assumption is violated, due to hardware inconsistency or inaccurate task devision startegy, the system enters a non-termination loop of failed attempts to reach the next task boundery. logically, better than relying on a rondom process, energy shots arrival, to break out of this loop, the system should execute an "emergency-like" routine to terminate it and preserve forward progress.

@@

\begin{itemize}
	\item Two adaptive coalescing strategies for selecting boundaries to coalesce based on past execution behaviour;
	\item Software memory virtualisation for transiently-powered devices that preserves atomicity of coalesced tasks;
	\item Task splitting startegy that preserve forward progress and memory consistency;
\end{itemize}
